What is a Scheme in Algebraic Geometry?

### 2020-11-25 blueprint.tex
Updates blueprint

\documentclass[12pt]{report}

@@

\title{Blueprint}
\author{Anthony Bordg}
\date{\today}
\maketitle

@@

@@

@@

@@

\chapter{Commutative Algebra}
\label{chap:commalg}

\section{Fields}
\label{sec:fields}

>>>>

\documentclass[12pt]{article}

@@

\title{What is a Scheme in Algebraic Geometry?}
\author{Anthony Bordg}
\date{\today}
\maketitle

\begin{abstract}
% To be completed	
\end{abstract}

@@

\begin{definition}[morphism of presheaves of rings]
	A morphism $\phi: \mathscr{F} \rightarrow \mathscr{F}'$ of sheaves of rings on a topological space $X$ is given by a morphism $\phi_U: \mathscr{F}(U) \rightarrow \mathscr{F}'(U)$ for each open subset $U$ of $X$ such that  the following diagram commutes
	\[
	\begin{tikzcd}
	\mathscr{F}(U) \arrow[r, "\phi_U"] \arrow[d, "\rho_{UV}"] & \mathscr{F}'(U) \arrow[d, "\rho'_{UV}"] \\
	\mathscr{F}(V) \arrow[r, "\phi_V"] & \mathscr{F}'(V) 
	\end{tikzcd}
	\]
	for every inclusion $V \subseteq U$. \\
	An isomorphism of presheaves is a morphism which has a two-sided inverse.
\end{definition}

@@

\begin{definition}[morphism of sheaves of rings]
	A morphism of sheaves of rings is a morphism of presheaves of rings.
\end{definition}

\begin{cons}
	Let $f: X \rightarrow Y$ be a continuous map between topological spaces and $\mathscr{F}$ a sheaf of rings on $X$. Given an open subset $V$ of $Y$, define $(f_{*} \mathscr{F})(V)$ to be $\mathscr{F} (f^{-1}(Y))$.  
\end{cons}

\begin{ex}
	Prove $f_{*} \mathscr{F}$ above is a sheaf of rings on the topological space $Y$.  
\end{ex}

\begin{definition}[direct image sheaf]
	Let $f: X \rightarrow Y$ be a continuous map between topological spaces and $\mathscr{F}$ a sheaf of rings on $X$. The sheaf $f_{*} \mathscr{F}$ is the direct image of $\mathscr{F}$. 
\end{definition}

@@

\begin{definition}[ringed space]
	A ringed space is a pair $(X, \mathscr{O}(X))$, where $X$ is a topological space and $\mathscr{O}(X)$ is a sheaf of rings on $X$.
\end{definition}

\begin{definition}[morphism of ringed spaces]
	A morphism of ringed spaces from $(X, \mathscr{O}(X))$ to $(Y, \mathscr{O}(Y))$ is a pair $(f, f^{\sharp})$ consisting of a continuous map $f: X \rightarrow Y$ between topological spaces and a morphism $f^{\sharp}: \mathscr{O}_Y \rightarrow f_{*} \mathscr{O}_X$ of sheaves of rings.   
\end{definition}

\begin{definition}[locally ringed space]

\end{definition}

\begin{ex}
	Prove $(Spec R, \mathscr{O})$ is a locally ringed space.
\end{ex}

\begin{definition}[morphism of locally ringed spaces]

\end{definition}

\begin{definition}[affine scheme]
	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic to the spectrum $(Spec R, \mathscr{O})$ for some ring $R$. 
\end{definition}

\begin{definition}[scheme]

\end{definition}

@@

\section{Solutions of exercises}

% To be completed

%\section{Commutative Algebra}
%\label{chap:commalg}

%\subsection{Fields}
%\label{sec:fields}
